HO unification from object language to meta language

### 2024-04-03 paper/main.tex
tex: rework maybebeta

\todo[inline]{IIRC, second order unification, where variables can stand for functions, is semi-decidable, indeed Huet's algorith enumerates all solutions. Third order, functions that take functions, is undecidable, proved by Dowek. IMO here the problem is that there is no unique solution, (semi)decidability is a secondary point. This paragraph needs fixing.}
Until now, we have only dealt we unification of terms in \llambda. However, we
want the unification relation to be more robust so that it can work with terms
in \maybebeta. Unification in \maybebeta is in general a non-decidable
procedure, e.g. $X \appsep a \Uo a$ is a unification problem in \maybebeta,
since we have $X a$ has the shape $X t_1\dots t_n$ where $X$ is a unification
variable and $t_1\dots t_n$ is not a list of distinct names (in our example, $a$
is a constant, hence not a name). We also point out that this unification
problem admits two different substitutions: $\rho_1 = \{X \mapsto \lambda x.x\}$
and $\rho_2 = \{X \mapsto \lambda \_.a\}$.

It is the case, however, given a list of unification $n$ problems \foUnifPb, if
$\foUnifPb_i$ is in \maybebeta, it is possible that the resolution of the
problems $\bigwedge_{j=0}^{i-1}\foUnifPb_j$ gives a partial substitution
$\rho$, such that $\rho\foUnifPb_i$ falls again in \llambda.
%
% make test ONLY=7003 TEX=TEX + deactivate beta tex
\printAlll
  {{{X,\lambda x.Y},
    {(X\appsep a),a}}}
  {{{A,\lambda x.B},
    {(A\appsep a),a}}}
  {{{Y,B,0},
    {X,A,0}}}
  {{}}

>>>>

\todo[inline]{IIRC, second order unification, where variables can stand for functions, is semi-decidable, indeed Huet's algorith enumerates all solutions. Third order, functions that take functions, is undecidable, proved by Dowek. IMO here the problem is that there is no unique solution, (semi)decidability is a secondary point. This paragraph needs fixing.}
Until now, we have only dealt we unification of terms in \llambda. However, we
want the unification relation to be more robust so that it can work with terms
in \maybebeta. In general, unification in \maybebeta admits more then one
solution and commiting one of them in the substitution does not guarantee
prop.~\ref{prop:complete}. For instance, $X \appsep a \Uo a$ is a unification
problem admits two different substitutions: $\rho_1 = \{X \mapsto \lambda x.x\}$
and $\rho_2 = \{X \mapsto \lambda \_.a\}$. Prefer one over the other may break
future unifications.

It is the case that, given a list of unification problems, $\foUnifPb_1\dots
\foUnifPb_n$ with $\foUnifPb_n$ in \maybebeta, the resolution of
$\bigwedge_{i=0}^{n-1}\foUnifPb_i$ gives a partial substitution $\rho$, such
that $\rho\foUnifPb_n$ falls again in \llambda.
%
% make test ONLY=7003 TEX=TEX + deactivate beta tex
\printAlll
  {{{X,\lambda x.Y},
    {(X\appsep a),a}}}
  {{{A,\lambda x.B},
    {(A\appsep a),a}}}
  {{{Y,B,0},
    {X,A,0}}}
  {{}}
